Per captia consumption

### 2021-06-15 NOBA_cod_files/README.Rmd

### Convert SAM inputs to SS inputs
```{r, warning = FALSE, message = FALSE}
# Set up two scenarios
# Scenario A: use selectivity pattern 12 and F method 3 in SS
# Scenario B: use selectivity pattern 12 and F method 2 in SS

scenario_path <- c("A", "B")
slx_pattern <- c(12, 12)
f_method <- c(3, 2)

@@

ss_output <- list()
for (scenario_id in seq_along(scenario_path)){
  ss_output_path <- here::here("NOBA_cod_files", "output", scenario_path[scenario_id])
  ss_output_data <- SS_output(dir = ss_output_path, verbose = F, printstats = F)
  ss_output[[scenario_id]] <- data.frame(
    "Year" = sam_output$Year,
    "SSB" = ss_output_data$timeseries$SpawnBio[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Recruits" = ss_output_data$timeseries$Recruit_0[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "F" = ss_output_data$timeseries$`F:_1`[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Catch" = ss_output_data$timeseries$`sel(B):_1`[ss_output_data$timeseries$Yr %in% sam_output$Year]
  )
}

>>>>

### Convert SAM inputs to SS inputs
```{r, warning = FALSE, message = FALSE}
# Set up two scenarios
# Scenario A: use selectivity pattern 20 and F method 3 in SS
# Scenario B: use selectivity pattern 20 and F method 2 in SS

scenario_path <- c("A", "B")
slx_pattern <- c(20, 20)
f_method <- c(3, 2)

@@

ss_output <- list()
for (scenario_id in seq_along(scenario_path)){
  ss_output_path <- here::here("NOBA_cod_files", "output", scenario_path[scenario_id])
  ss_output_data <- SS_output(dir = ss_output_path, verbose = F, printstats = F)
  ss_output[[scenario_id]] <- data.frame(
    "Year" = sam_output$Year,
    "SSB" = ss_output_data$timeseries$SpawnBio[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Recruits" = ss_output_data$timeseries$Recruit_0[ss_output_data$timeseries$Yr %in% (sam_output$Year-1)],
    "F" = ss_output_data$timeseries$`F:_1`[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Catch" = ss_output_data$timeseries$`sel(B):_1`[ss_output_data$timeseries$Yr %in% sam_output$Year]
  )
}
